\Title

### 2020-11-03 manuscript/manuscript.tex
Move new section after "Source distributions"
Improve math and move section as a subsection of EQL technique

@@

\section{Iteratively fitting source coefficients}

Following equation \ref{eq:linear-problem} lets assume we have $N$ measurements
of a harmonic field on observations points $\{\mathbf{p}_i\}_{i=1}^{N}$ stored in
the vector $\mathbf{d} = (d_1, d_2, \ldots, d_N)^T$. We have defined a set of
$M$ point sources located on $\{\mathbf{q}_j\}_{j=1}^{M}$, whose coefficients
$\mathbf{c} = (c_1, c_2, \ldots, c_M)^T$ must be fitted so they can minimize
the misfit function defined on \ref{eq:misfit-unscaled}.

By defining a set of $K$ overlapping windows we can simplify the linear problem:

\begin{equation}
    \mathbf{d}
    = \mathbf{A} \mathbf{c}
    = \mathbf{A} \left( \sum_{k=1}^K \mathbf{c}_k \right)
    = \sum_{k=1}^K \mathbf{A} \mathbf{c}_k,
\end{equation}

\noindent where $\mathbf{c}_k$ are vectors full of zeros except those $m_k$
elements corresponding to the sources $\mathbf{q}_j$ that fall inside the
window $k$.

By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
independently and iteratively by defining a residue vector $\mathbf{r}_k$ that
it's initialized with the observed data and updated on each iteration:

\begin{equation}
    \mathbf{r}_k = \mathbf{r}_{k-1} - \mathbf{A}\mathbf{c}_k.
    \label{eq:residue}
\end{equation}

\noindent On each iteration the $\mathbf{c}_k$ vectors can be fitted so they
minimize the misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \mathbf{d} - \mathbf{A}\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

Because the $\mathbf{c}_k$ vector has only $m_k$ non-zero elements, the linear
system can be greatly simplified:

\begin{equation}
    \begin{split}
        \mathbf{A}\mathbf{c}_k = &
        \overbrace{
            \begin{bmatrix}
                a_{11} & a_{12} & a_{13} & \cdots & a_{1M} \\
                a_{21} & a_{22} & a_{23} & \cdots & a_{2M} \\
                a_{31} & a_{32} & a_{33} & \cdots & a_{3M} \\
                \vdots  & \vdots  & \vdots  & \cdots & \vdots \\
                a_{N1} & a_{N2} & a_{N3} & \cdots & a_{NM}
            \end{bmatrix}
        }^\text{$N \times M$ elements}
        \cdot
        \overbrace{
            \begin{bmatrix}
                0 \\
                {c_k}_2 \\
                0 \\
                \vdots  \\
                {c_k}_M \\
            \end{bmatrix}
        }^\text{$M$ elements}
        = \\ = &
        \underbrace{
            \begin{bmatrix}
                a_{12} & \cdots & a_{1M} \\
                a_{22} & \cdots & a_{2M} \\
                a_{32} & \cdots & a_{3M} \\
                \vdots  & \cdots & \vdots \\
                a_{N2} & \cdots & a_{NM}
            \end{bmatrix}
        }_\text{$N \times m_k$ elements}
        \cdot
        \underbrace{
            \begin{bmatrix}
                {c_k}_2 \\
                \vdots  \\
                {c_k}_M \\
            \end{bmatrix}
        }_\text{$m_k$ elements}
        = \tilde{\mathbf{A}} \tilde{\mathbf{c}}_k
        .
    \end{split}
\end{equation}

By removing the columns of the $\mathbf{A}$ matrix that are not needed in the
$k$-th iteration we greatly reduce the memory consumption to solve the linear
problem. Nevertheless, if the number of observation points ($N$) is too large,
the $\tilde{\mathbf{A}}$ matrix might be large enough for the available memory.

One more simplification can be carried out by ignoring the effect of the $m_k$
sources on the observation points that fall outside the $k$ window. This means
that the coefficients $\mathbf{c}_k$ will be fitted only taking into account
the data values on the $n_k$ observation points that fall inside the same
$k$-th window.
This allows to reduce the $\tilde{\mathbf{A}}$ matrix to a $\mathbf{B}$ matrix
with $n_k \times m_k$ elements:

\begin{equation}
    \mathbf{B} \tilde{\mathbf{c}}_k
    =
    \underbrace{
        \begin{bmatrix}
            a_{32} & \cdots & a_{3M} \\
            \vdots  & \cdots & \vdots \\
            a_{N2} & \cdots & a_{NM}
        \end{bmatrix}
    }_\text{$n_k \times m_k$ elements}
    \cdot
    \underbrace{
        \begin{bmatrix}
            {c_k}_2 \\
            \vdots  \\
            {c_k}_M \\
        \end{bmatrix}
    }_\text{$m_k$ elements}
    .
\end{equation}

These two simplifications help to greatly reduce the size of the linear
problem, reducing it to:

\begin{equation}
    \mathbf{d}_k = \mathbf{B} \tilde{\mathbf{c}}_k,
\end{equation}

\noindent where $\mathbf{d}_k$ is a vector containing only the measured data
values corresponding to the observation points that fall inside the $k$-th
window.
This linear problem can be solved using the same method described on Section
\ref{sec:eql-implementation}, obtaining values for the $\mathbf{c}_k$
coefficients and updating the residual through equation \ref{eq:residue}, i.e.
taking into account the effect of the fitted coefficients on every observation
point.
Worth noting that for updating the residue there's no need of computing the
entire Jacobian matrix.

After passing through every $K$ window, the residue $r_K$ should be
sufficiently small obtaining a set of source coefficients as the sum of the
$\mathbf{c}_k$ vectors:

\begin{equation}
    \mathbf{c} = \sum_{k=1}^K \mathbf{c}_k
\end{equation}

Shuffle the windows.

First we define a set of equivalent sources following one of the
source distributions described on the previous sections, e.g. the block-reduced
sources at variable depth. Secondly we define a set of overlapping moving
windows that cover the entire area of the data. Then we start the iterative
process: on each iteration we choose one window and select every data points
and sources that fall inside it, compute the Jacobian elements corresponding to
these subsets of data points and sources, fit the coefficients of the chosen
sources and finally remove the effect of these sources from the entire data,
obtaining a \emph{residue}. On the following iterations the same process is
carried out, but now the coefficients are fitted using the residue instead of
the original data.

>>>>

\subsection{Gradient boosted equivalent sources}

Lets assume we have $N$ measurements of a harmonic field on observations points
$\{\mathbf{p}_i\}_{i=1}^{N}$ stored in the vector $\mathbf{d} = (d_1, d_2,
\ldots, d_N)^T$. We have defined a set of $M$ point sources located on
$\{\mathbf{q}_j\}_{j=1}^{M}$. Instead of trying to fit the entire set of
coefficients $\mathbf{c}$ at once, we can reduce the problem to fitting $K$
different sets of equivalent sources: we define $K$ overlapping windows of
equal size that cover the whole observation area, and then we create one set of
equivalent sources per window formed by the $\{\mathbf{q}_m\}_{m=1}^{M_k}$
sources that fall inside the $k$-th window.
The observed data should be equal to the superposition of the
effect of every set of equivalent sources:

\begin{equation}
    \mathbf{d} = \sum_{k=1}^K \mathbf{A}_k \mathbf{c}_k,
\end{equation}

\noindent where $\mathbf{c}_k$ is the vector of coefficients for the $k$-th
set of equivalent sources and $\mathbf{A}_k$ is the Jacobian matrix between
those sources and every data point.

By applying gradient boosting we can fit each $\mathbf{c}_k$ vector
iteratively: on each iteration a residue vector $\mathbf{r}_k$ (initialized
with the observed data) is used to fit the $\mathbf{c}_k$
coefficients and then updated by removing the effect of the same sources, as
follows:

\begin{equation}
    \mathbf{r}_k = \mathbf{r}_{k-1} - \mathbf{A}_k\mathbf{c}_k.
    \label{eq:residue}
\end{equation}

\noindent On each iteration the $\mathbf{c}_k$ vectors can be fitted so they
minimize following misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \mathbf{r}_{k-1} - \mathbf{A}_k\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

\noindent following the same method described on Section
\ref{sec:eql-implementation}.
Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
adjusting the size of the overlapping windows can help in reducing the computer
memory needed to fit the source coefficients and ultimately to interpolate the
observed data.

Nevertheless, in case our observed data is too large that even the
$\mathbf{A}_k$ matrices cannot be stored into memory, we can apply one more
simplification on the fitting process: ignore the effect of any observation
point outside the $k$-th window while fitting the sources that fall under the
same window.

Assuming that there are $N_k$ observation points that fall under the $k$-th
window, we can fit the $\mathbf{c}_k$ coefficients by minimizing the following
misfit function:

\begin{equation}
    \phi(\mathbf{c}_k) =
        \left\lVert
            \tilde{\mathbf{r}}_{k-1} - \tilde{\mathbf{A}}_k\mathbf{c}_k
        \right\rVert ^ 2
        + \lambda_d \left\lVert \mathbf{c}_k \right\rVert ^2,
\end{equation}

\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
observation points that fall under the $k$-th window, and
$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between the observation points
and sources that fall under the same window.
Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
elements, the computer memory needed for fitting the $\mathbf{c}_k$
coefficients is greatly reduced.

Once the $\mathbf{c}_k$ coefficients are fitted, equation \ref{eq:residue} is
applied to update the residue, i.e. the effect of the sources belonging to the
$k$-th window is computed on every observation point. Worth noting that while
calculating the effect of the sources we don't need to pre-compute the entire
Jacobian matrix: the effect of the sources on each observation point can be
carried by a simple addition of terms, computing each Jacobian element at once
when needed.

Because the number of windows is fixed before starting the iteration process,
its number of steps are also fixed to $K$. Moreover, the windows are randomly
shuffled before starting the process to prevent that any particular
sets of equivalent sources are prioritized over the rest.

After all $\mathbf{c}_k$ coefficients vectors are fitted, we can predict the
effect of every equivalent source on any point as follows:

\begin{equation}
    V(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{m=1}^{M_k}
    \frac{{c_k}_m}{|\mathbf{p} - \mathbf{q}_m|}.
\end{equation}

@@
